\documentclass[a4paper,12pt]{article}
\usepackage{amssymb} % needed for math
\usepackage{amsmath} % needed for math
\usepackage[T1]{fontenc}    % this is needed for correct output of umlauts in pdf
\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{listings} % needed for the inclusion of source code
\usepackage{minted}
\usepackage{tabu}
\usepackage{pdfpages}
\usepackage{tabularx} % in the preamble
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{caption}
\usepackage{rotating}
\usepackage[utf8]{inputenc}
\usetikzlibrary{shapes,arrows}

\title{2018 Part IV Power Systems Projects - Project 109}
\author{Timothy Lopez, Danyon Wye}
\date{29 March 2018}

\begin{document}

\maketitle
% \subject {Minutes of Meeting}\\
% \\A meeting of the Project 109 Team held in 401.709 at 1230-1330 hours. 

% \maketitle
% \subject {Present}\\
% \\Professor Nirmal Nair (Supervisor), Mr Abhinav Rakesh Chopra (Secondary Supervisor), Danyon Wye, Timothy Lopez.

\section{Minutes of Meeting}
A meeting of the Project 109 Team held in 401.709 at 1230-1330 hours.

\section{Present}
Professor Nirmal Nair (Supervisor), Mr Abhinav Rakesh Chopra (Secondary Supervisor), Danyon Wye, Timothy Lopez.


\section{Apologies}
Apologies were received from: Dr Mohammad Javad Sanjari


\section{Minutes Of Last Meeting}
Initial Meeting Minutes.


\section{Agenda and Discussions}
\begin{enumerate}
    \item Literature Review: Briefly covered the specifications of the Literature Review Report in regards to separate submissions, report layout and consideration for separation of duties. The report is 10 pages with 2-3 pages for references (inclusive) of which 50\%~ should be IEEE.   
    \item Research Scope: Advised to broaden the scope of research with less focus on implementation at this stage. Focus should be model based looking at various models which have separate central focuses(Security, Privity, Scalability etc.). Also consider the size of systems (Neighbourhoods, blocks, Personal Homes) and the commercial or personal use of the model. Other considerations can be made regarding regulation and impediments these can be touched on in report but should not be a primary focus.  
    \item : Implementation: Prof. Nirmal Nair and the department work closely with various companies and can provide a gateway for testing and implementation in the latter half of the project as well as access to accurate statistics for NZ energy. Consideration should be given to a possible physical prototype. Again this is will be focused on in the implementation stage post Literature Review. 
\end{enumerate}

\section{Resource Needs}
2017 Project Paper may be released after the Literature Review. 

\section{Date of Next Meeting}
The next meeting to be held in 303.312 and is set for 5th April 2018 at 1200 hours.


\end{document}
